A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice

### 2020-01-29 0_reviewer_response.tex

\Que{
Finally, the examples provided depict the results obtained by the authors by "emulating" other techniques, but not with the actual results produced by the other techniques. While the reason behind this choice is easy to guess, it weakens the effectiveness of the claims. Adding careful discussions/extensions to support these questions would make the paper stronger.
}
\Ans{
We've added a paragraph to section~5.4~Limitations, which discusses these emulation limitations.
}
\commits{
639dccad8e97fa1f0bdbb28e16b64f587572792d % paragraph in limitations
}
\paper{5.4 Limitations}
{
\revise{}{
Finally it should be noted that although our framework can accurately emulate the constant bead count approach by \citeauthor{Ding2016a}, its emulation of the centered approach by \citeauthor{Jin2017JMS} is imperfect.
The transitions resulting from out framework introduce sharper corners and there is more width variation in those corners.
Whereas the width of the connecting segment in the approach by \citeauthor{Jin2017JMS} is the preferred width $w^*$, the bead widths closer to the center resulting from our framework will be twice the local radius, which is larger than $w^*$.
However, this inflated bead width variation is expected to have an insignificant impact on the measured bead width variation.
}
}

\section{Reviewer 3}
\Summary{
Paper is well written. It is mostly easy to follow but overall, I find the the contributions somewhat incremental and the motivation not convincing. The paper mostly feels like a technical report. I am not sure if the methods overall teach enough to the researchers in the field to open up new research possibilities. My specific comments are below: 
}
\Ans{
Thank you for your feedback.

}

\Que{
The title is a little misleading that the presented approach may be used for general “Additive Manufacturing”. However, my understanding from the text is that it is designed particularly for FDM. I believe it is important to highlight this in the title. Otherwise, there should be enough evidence to prove that it can be applied to other kinds of printing processes, such as SLS, SLA, DMLS etc. 
}
\Ans{
The title has changed.
}
\commits{
64eb2f2c1cbb28258a984b5f84ea6e3a039ee1f0
1935689874235a6c1d5b8f0fed725afa53804935 % don't introduce only one strategy for FDM only
56bbbaf0b6de98f6e6d4b4fa849ee17cf98e4b3a % remove `for FDM'
}
\paper{Title}{
A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}
}
\paper{Abstract}
{
Furthermore, we propose a novel scheme\revise{ for FDM printing} which [\dots]
}
\paper{1. Introduction, bullet list}{
A specific beading scheme \revise{for FDM printing}{} which [\dots]
}

@@

\Que{
It would be nice to discuss why contour-parallel toolpaths are needed or selected. In what situations, these are required as opposed to zigzag style (or direction-parallel as referred in the text) patterns. Without such a discussion, the motivation seems a little weak. In the second paragraph of introduction, there is a short discussion about this but it sounds like the authors assume that even the perimeters (or outline) are printed with direction-parallel extrusion. However, common approach in FDM is to print the perimeters with contour parallel toolpaths and fill the inner region with direction-parallel paths only (as later acknowledged in the related work 3rd paragraph). I think the motivation for contour parallel toolpaths needs to be justified further. 
}\label{outline_question}
\Ans{
The industry standard is to use a combination of contour-parallel and direction-parallel.
Our approach was developed to improve on the former part while keeping the latter intact -- not to replace the latter by the former.

We now clarify why contour-parallel is (partly) used and that \emph{in as much as contour-parallel is used}, our approach improves on the industry standard.
We have also developed and presented a new meta-scheme for generating only a limited number of perimeters, which shows that our technique is compatible with generating direction-parallel toolpaths for internal areas.
See also the changes to the paper presented under question~\ref{widening_question}.
}

\commits{
6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae % clarify widespread use of concentric toolpaths in abstract (reviewer 3.9)
ac800628951417dcb28bd6e3a0ed08801735acf4 % emphasize importance of contour-parallel toolpaths (reviewer 3.2)
a88ccd3309aef1233ed00ce9f22b244fe64668f4 % introduce shell meta-scheme and replace widening figure with widening+shell figure 
077c8ee138bb311a8ba9abf303af4b09e973637a % improve introduction of contour-parallel (reviewer 3.2)
8a11aa0105d1c7f1f5690c8e1f932be85a90bcae % more changes to shell + widening fig
fc6e05c79340dafd15a9f95de175de696c427513 % explain contour vs direction parallel better
7a2b37513a940ea71a54be05075e46157084b40b % in related work
}
\paper{Abstract}{
\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
{High stiffness parts are produced by filling the 2D polygons of consecutive layers with contour-parallel extrusion toolpaths.}
}

### 2020-01-29 6_validation.tex
commit tags in response

\subsubsection{Uniformity}
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
\revise{
We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
}{
We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
}
We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme. 
These results show that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
\revise{
We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.
}{}

>>>>

\subsubsection{Uniformity}
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
\revise{
We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
}{
We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
}
We found that the mean width of the inward and evenly distributed schemes is close to \revise{}{the }preferred bead width of \revise{\SI{400}{\micro\meter}}{\SI{0.5}{\milli\meter}}, while their standard deviation is lower than for the centered and constant bead count scheme. 
These results show that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
\revise{
We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.
}{}
